---
title: "Readme_and_Examples"
author: "Thomas FitzGerald"
date: "12/31/2022"
output: html_document
editor_options: 
  markdown: 
    wrap: 72
---

# Summary

This is part of an ongoing project to develop a Twitter Dashboard for
the Tampa Bay Estuary Program on environmental issues. The associated
files are part of Stage 1, which focuses on topic viability, and
developing a workflow for query development.

# Directory Contents

The directory containing this file should contain the following files:
  * $twitter\_functions.R$: Contains the functions demonstrated here.
  * $queries.R$: Contains pre-defined search queries. Variables are named
'$queries.x$' 
  * $location\_terms.R$: Contains pre-defined location terms to add
to queries. Variables are named '$locations.x$' 
  * $search\_terms.R$: Contains search terms related to the queries in $queries.R$. Variables are named
'$terms.x$'

```{r}
source("Project_Functions.R")
source("queries.R")
source("Project_Objects.R")
#source("location_terms.R")
```

#Setup ***IMPORTANT: token.R is not included, and defines the
bearer_token variable. You will need to add bearer_token manually.***

```{r}
#One of these two options:
source("Bearer_Token.R") #(defines bearer_token)
#bearer_token = 

headers = c(
  `Authorization` = sprintf('Bearer %s', bearer_token)
)
```

Required Libraries:

```{r Libraries, include=FALSE}
library(httr)
library(dplyr)
library(plotly)
```

# Function Walkthrough

This document will walk you through example use-cases for all the
functions in $twitter\_functions.R$:

  * $set\_parameters$: Formats input for query_twitter or query_twitter_count.
  * $query\_twitter\_count$: Returns a count of tweets matching criteria.
  * $query\_twitter$: Retrieves tweets matching search criteria.
  * $query\_graph\_comparison$: Prints & returns a plotly line plot of tweet counts over time between two queries. 
  * $query\_text\_comparison$: Used for comparing tweets returned by two queries

# set_parameters()

$set\_parameters()$ creates a parameter list that can be fed into
$query\_twitter()$ or $query\_twitter\_count()$. If you omit end.date, queries
will return all results from start.date, so the only required arguments
are '$query.text$', and '$start.date$'.

# query_twitter_count()

$query\_twitter\_count()$ returns the \# of tweets in a date range.

```{r}
query.text<-'leachate'
start.date<-'2022-09-01'
end.date<-'2022-09-02'
params<-set_parameters(query.text,start.date,end.date)
query_twitter_count(params)
```

# query_twitter

$query\_twitter()$ can be used with the same parameters to retrieve the
actual tweets:

```{r}
# Feel free to uncomment and run it

# query_twitter(params)
```

By default, the follow fields are retrieved: 
  * $tweet.fields$: $id$, $text$, $created\_at$, $author\_id$, $lang$
  * $user.fields$: 
  * location expansions:
  * expansions: $author\_id$ 'joins' the two, where
$tweet.fields.author_id=user.fields.id$. 

You can also get additional
fields using $set\_parameters()$ by editing the $tweet.fields$ and
$user.fields$ parameters:

```{r}
query.text<-'leachate'
start.date<-'2022-09-01'
end.date<-'2022-09-02'

params<-set_parameters(query.text=query.text,
                       start.date=start.date,
                       end.date=end.date,
                       tweet.fields='author_id,created_at,lang,attachments,context_annotations,conversation_id,entities,geo,in_reply_to_user_id,possibly_sensitive,public_metrics,referenced_tweets,reply_settings,source,withheld', #id/text are automatic
                       user.fields='location,description,entities,pinned_tweet_id,profile_image_url,public_metrics,url,verified,withheld', #name/username are automatic
                       expansions='author_id')


# Feel free to uncomment and run it

# query_twitter(params,iter.limit=1)
```

(Scroll over to check the additional variables)

Above is not a comprehensive list. For more options, check out:
<https://developer.twitter.com/en/docs/twitter-api/fields>
<https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/tweet>
<https://developer.twitter.com/en/docs/twitter-api/data-dictionary/object-model/user>

Some pre-defined queries & location terms are also imported from the
$source()$ commands in the first block of this document. All these
variables start with '$queries.$' or '$locations.$', so you can pull them up
with auto-complete. \*Make sure to use $sep=' '$, or it may generate a
syntax error in the query. There's no error message when this happens,
it just returns 0 results.

```{r}
query.text<-queries.deepwellinjection
query.text<-paste(query.text,area.terms[["Tampa"]],sep=' ')
query.text
```

```{r}
params<-set_parameters(query.text,'2022-08-28')

# Feel free to uncomment and run it
# query_twitter_count(params)
```

Besides the above, there are also two functions specifically for
comparing query results.

# location terms

Query terms that indicate location mentions:

```{r}
#All Location Terms
locations.all<-'-(-tampa -bradenton -bradentonbeach -clearwater -clearwaterbeach -hillsborough -manatee_county -pasco -pinellas -sarasota -siesta_key -st_pete -st_petersburg -apollo_beach -gibsonton -ruskin -wimauma -sun_city -hillsborough_bay -indian_rocks_beach -tarpon_springs -belleair -palm_harbor -safety_harbor -dunedin -honeymoon_island -sand_key -caladesi -lake_tarpon -madeira_beach -treasure_island -sunshine_skyway -redington -fort_de_soto -fort_desoto -pass_a_grille -boca_ciega_bay -anna_maria_island -longboat_key -holmes_beach -manatee_river -port_manatee -(coquina_beach -NC -carolina) -venice -englewood -north_port -casey_key -nokomis -lemon_bay -st_armands -manasota_key -manasota_beach -englewood_beach -lido_key -lido_beach -port_richey -bayonet_point -anclote -cottee_river)'

#Primary Locations Terms
locations.primary<-'-(-tampa -bradenton -bradentonbeach -clearwater -clearwaterbeach -hillsborough -manatee_county -pasco -pinellas -sarasota -siesta_key -st_pete -st_petersburg)'

#Secondary Location Terms (all)
locations.secondary.all<-'-(-apollo_beach -gibsonton -ruskin -wimauma -sun_city -hillsborough_bay -indian_rocks_beach -tarpon_springs -belleair -palm_harbor -safety_harbor -dunedin -honeymoon_island -sand_key -caladesi -lake_tarpon -madeira_beach -treasure_island -sunshine_skyway -redington -fort_de_soto -fort_desoto -pass_a_grille -boca_ciega_bay -anna_maria_island -longboat_key -holmes_beach -manatee_river -port_manatee -(coquina_beach -NC -carolina) -venice -englewood -north_port -casey_key -nokomis -lemon_bay -st_armands -manasota_key -manasota_beach -englewood_beach -lido_key -lido_beach -port_richey -bayonet_point -anclote -cottee_river)'
```

# query_graph_comparison()

$query\_graph\_comparison()$ runs $query\_twitter\_counts()$ for both queries,
then produces a plotly lineplot of the results. This one runs fast, and
is good for getting an overview of activity in a time frame.

**The same query with different sets of location terms**

```{r}
query.text.1<-paste(main.queries[["IndustrialSpill"]],locations.primary,sep=' ')
query.text.2<-paste(main.queries[["IndustrialSpill"]],locations.secondary.all,sep=' ')
query_graph_comparison(start.date='2022-09-01',
                       end.date='2022-09-30',
                       query.text.1=query.text.1,
                       query.text.2=query.text.2,
                       topic_1='Primary Location Terms',
                       topic_2='Secondary Location Terms')
```


**Similar topical queries (industrial and sewage spills), with the same set of location terms**

```{r}

query.text.1<-paste(main.queries[["IndustrialSpill"]],locations.primary,sep=' ')
query.text.2<-paste(main.queries[["SewageSpill"]],locations.primary,sep=' ')
query_graph_comparison(start.date='2022-07-01',
                       end.date='2022-07-31',
                       query.text.1=query.text.1,
                       query.text.2=query.text.2,
                       topic_1='Wastewater',
                       topic_2='Sewage')
```



# query_text_comparison() 

$query\_text\_comparison()$ runs $query\_twitter()$ for both queries, then
compares the results. This one is slower, and is better used on short
date ranges. Let's use July 1st-31st 2022 for the plot, since both queries
had heightened activity those day:

It returns a list of 4 dataframes: 
  * [1] - Query 1's results 
  * [2] - Query 2's results 
  * [3] - Results found in both query's results 
  * [4] - Text matching results

```{r}

terms.all <- c("wastewater", "contamin", "chemical", "stormwater", "storm water", "discharge", "pump", "tampa")

results.list<-query_text_comparison(start.date = '2022-07-01',
                                    end.date = '2022-07-31',
                                    query.text.1 = query.text.1,
                                    query.text.2 = query.text.2,
                                    topic_1 = 'Wastewater',
                                    topic_2 = 'Sewage'
                                   # , term.list = NULL
                                    , term.list = terms.all
  )

# Feel free to uncomment and run it
# results.list[1] #Query1 results only
# results.list[2] #Query2 results only
# results.list[3] #Tweets appears in both queries only

results.list[4] #Comparison
```
$results.list[4]$ works with the term.list argument for
$query\_text\_comparison()$. This returns the proportion of each query's
results that contain keywords. So, from the output above, one can notice that $45\%$ of tweets returned for the industrial spill query ($Query1$) had words with root "$contamin$" in it, while only $0.5\%$ had the word "$wastewater$". As far as location terms, $43\%$ of industrial spill tweets mentioned "$tampa$". For the sewage spill query ($Query2$), we had $50\%$ of tweets mention "$stormwater$", $30\%$ use words with root "$pump$", and $70\%$ of tweets contained mentions of "$tampa$".

Keep in mind that the bulk of your results may be retweets or quotes, so
the $50\%$ "$stormwater$" proportion could be heavily constituted of retweets emanating from one tweet.

---

I hope this document was useful to you. Please feel free to re-use any
of the templates above!
